TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2019-06-19 paper/draft.tex
topcat ref
add aitoff proj
comment out figure
caption edits

% ----------------------------------------
\subsection{Spectral Type Model \label{subsec:west_results}}

@@

@@

\begin{figure}
	\includegraphics[width=\linewidth]{figures/cannon_vs_parsec.png}
	\includegraphics[width=\linewidth]{figures/aspcap_vs_parsec1.png}
	\caption{Comparison of \cannon\ $\feh$ as compared to metallicity predicted by PARSEC isochrone tracks \citealt{Bressan:2012} in \gaia\ color-magnitude space. The four panels show five metallicity tracks (ranging $-0.5<$[M/H]$<0.5$) over varying ages (3 and 7 Gyr).}
	\label{fig:isochrone_cmd}
\end{figure}

\begin{figure}
	\includegraphics[width=\linewidth]{figures/aspcap_vs_parsec2.png}
	\caption{}
\end{figure}

\begin{figure*}
	\plotone{figures/aspcap_cannon_label_hist.png}
	\caption{Distribution of temperatures and metallicities for 10,311 sources from \thecannon\ compared to the ASPCAP pipeline. Note that \cannon\ temperatures only span $2850<T_{\rm eff}<4150$ and $-0.5<\feh<0.5$\,dex because we have imposed cutoffs for stars that fall outside of the training sample range, however for the same 10,311 stars ASPCAP predicts temperatures with slightly higher temperatures and metallicities.}
	\label{fig:aspcap_cannon_label_hist} 
\end{figure*}

@@

\software{
	\code{Astropy} \citep{astropy,astropy2}, \,
	\code{matplotlib} \citep{Hunter:2007}, \,
	\code{numpy} \citep{vanderWalt:2011}, \,
	\code{scipy} \citep{Jones:2001}, \,
	\code{The Cannon} \citep{Ness:2015}}

@@

\begin{figure*}[h]
	\plotone{figures/mann_radii.png}
	\caption{Comparison of radii estimated from M15 relations: on the x-axis radii are derived from  K magnitudes and \cannon\ $\feh$, on the y-axis radii are derived from \cannon\ $\teff$ and $\feh$.}
	\label{fig:radii}
\end{figure*}

>>>>

@@

\subsection{Spectral Type Model \label{subsec:west_results}}

\begin{figure*}
	\includegraphics[width=\linewidth]{figures/aitoff.png}
	\caption{Aitoff projection of 14,827 sources.}
	\label{fig:aitoff}
\end{figure*}

@@

\begin{figure}
	\includegraphics[width=\linewidth]{figures/cannon_vs_parsec.png}
	\includegraphics[width=\linewidth]{figures/aspcap_vs_parsec1.png}
	\caption{Comparison of \cannon\ $\feh$ as compared to metallicity predicted by PARSEC isochrone tracks \citep{Bressan:2012} in \gaia\ color-magnitude space. The two panels show five metallicity tracks (ranging $-0.5<$[M/H]$<+0.5$ in steps of 0.1 dex) at two different ages (3 and 7 Gyr). In the ASPCAP plot only the 8,960 out of 10,311 sources with metallcities $-0.5<$[M/H]$<+0.5$ are shown, while the remaining 1,351 sources with [M/H]$<-0.5$ and [M/H]$>+0.5$ are shown separately in Figure \ref{fig:isochrone_cmd_2}.}
	\label{fig:isochrone_cmd}
\end{figure}

\begin{figure}
	\includegraphics[width=\linewidth]{figures/aspcap_vs_parsec2.png}
	\caption{}
	\label{fig:isochrone_cmd_2}
\end{figure}

\begin{figure*}
	\plotone{figures/aspcap_cannon_label_hist.png}
	\caption{Distribution of temperatures and metallicities for 10,311 sources from \thecannon\ compared to the ASPCAP pipeline. Note that \cannon\ temperatures only span $2850<T_{\rm eff}<4150$ and $-0.5<\feh<0.5$\,dex because we have imposed cutoffs for stars that fall outside of the training sample range, however for the same 10,311 stars ASPCAP predictions are skewed higher in temperature and lower in metallicity compared to \cannon\ measurements.}
	\label{fig:aspcap_cannon_label_hist} 
\end{figure*}

@@

\software{
	\code{Astropy} \citep{astropy,astropy2}, \,
	\code{matplotlib} \citep{Hunter:2007}, \,
	\code{numpy} \citep{vanderWalt:2011}, \,
	\code{scipy} \citep{Jones:2001}, \,
	\code{Topcat} \citep{Taylor2005}, \,
	\code{The Cannon} \citep{Ness:2015}}

@@

% \begin{figure*}[h]
% 	\plotone{figures/mann_radii.png}
% 	\caption{Comparison of radii estimated from M15 relations: on the x-axis radii are derived from  K magnitudes and \cannon\ $\feh$, on the y-axis radii are derived from \cannon\ $\teff$ and $\feh$.}
% 	\label{fig:radii}
% \end{figure*}
